---
title: "Class05"
author: "Kenneth Kelley"
date: "2026-09-09"
output:
  html_document:
    toc: true
    toc_float: true
    numbered_sections: true
    code_folding: true
    code_download: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Game 01: find your seat

campus = jsonlite::fromJSON(
  "https://isa401-find-your-seat.vercel.app/campus.json")
  
fsb = campus[['Farmer']]
fsb$code

fsb$floors
fsb$floors[[3]]$sections

campus = jsonlite::fromJSON(
  "https://isa401-find-your-seat.vercel.app/campus.json")
campus[["Farmer"]]$code                      # "MUFSB"
campus$Farmer$floors[["2"]]$sections        # 80
r = campus$Farmer$floors[["2"]]$rooms
r$isa_sections[r$room == "2050"]             # 11

getwd()

##read excel - I have no idea what happened here and why the first read excel didnt work
```{r}
occupation = readxl::read_excel(
  path = "Data/occupation.xlsx", sheet = "Table 1.4", skip = 1
)
```
occupation = readxl::read_excel(
  path = "Data/occupation.xlsx", sheet = "Table 1.4", skip = 1
)

occupation = readxl::read_excel(
  path = "Data/occupation.xlsx", sheet = "Table 1.4", skip = 1
)

occupation = occupation[-c(32,33,34),]


## JSON Data 

json_url = paste0(
  "https://data.cincinnati-oh.gov/",
  "resource/rvmt-pkmq.json?$limit=100")
crashes_json = jsonlite::fromJSON(json_url)
dplyr::glimpse(
  crashes_json[, c("crashdate", "dayofweek",
                   "crashseverity", "age")])

logins = readr::read_csv("https://isa401-import-heist.vercel.app/api/stage1?seat=R3-6&s=A")


log = jsonlite::fromJSON("https://isa401-import-heist.vercel.app/api/stage2?key=smithj31&seat=R3-6&s=A")
log$events$action
logevents = log$events$action
sum(logevents == "DOWNLOAD")


jsonlite::fromJSON("https://isa401-import-heist.vercel.app/api/finish?code=6&seat=R3-6&s=A")

